%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.1 2019-11-03
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Additional modifications by:
% Dylan Ashley
%
% Important note:
% This template requires the cv.cls file to be in the same directory as the
% .tex file. The cv.cls file provides the cv style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[a4paper,dateabbrev]{cv}

\name{Dylan Ashley}
\address{{\urlstyle{same} +41 78 213 19 50 ~ \\ ~ \href{mailto:mail@dylanashley.me}{mail@dylanashley.me} ~ \\ ~ \url{https://dylanashley.io}}}

\begin{document}

%----------------------------------------------------------------------------------------
%   EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Ph.D. in Informatics} \hfill \rDateRange{2021-01-04}{} \\[0.05em]
Universit{\`{a}} della Svizzera italiana (Dalle Molle Institute for Artificial Intelligence Research) \\[0.05em]
Supervisor: J{\"u}rgen Schmidhuber \\[0.05em]
Focus: Agentic AI, Creative Systems, Reinforcement Learning, Robotics, Neural Networks

%------------------------------------------------

{\bf M.Sc. in Computing Science} \hfill \rDateRange{2017-09-05}{2020-11-20} \\[0.05em]
University of Alberta (Alberta Machine Intelligence Institute) \\[0.05em]
Supervisor: Richard S. Sutton \textbf{(2024 Turing Award Recipient)} \\[0.05em]
GPA: 4.0 / 4.0

%------------------------------------------------

{\bf B.Sc. Honors in Computing Science} \hfill \rDateRange{2013-09-04}{2017-06-13} \\[0.05em]
University of Alberta

\end{rSection}

%----------------------------------------------------------------------------------------
%   WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{Research Scientist Intern}{\rDateRange{2026-06-01}{2026-11-13}}{Meta Platforms, Inc.}
    \item Conducted research at the Burlingame office under the supervision of Changsheng Zhang and Yangyang Shi on Agentic AI.
\end{rSubsection}

\begin{rSubsection}{Research Scientist Intern}{\rDateRange{2025-05-27}{2025-11-07}}{Meta Platforms, Inc.}
    \item Conducted research at the Z{\"u}rich office under the supervision of Ga{\"e}l Le Lan on Agentic AI.
    % \item Published [\ref{pub:ashley2026rpra}] based on work done.
    % \item Work location: Giessh{\"u}belstrasse 30, 8045 Z{\"u}rich, Switzerland.
\end{rSubsection}

\begin{rSubsection}{Visiting Researcher}{\rDateRange{2023-01-22}{}}{Center of Excellence in Generative AI, King Abdullah University of Science and Technology}
    \item Conducting research with Prof.\ Eric Feron and Prof.\ J{\"{u}}rgen Schmidhuber on several topics related to deep learning and robotics.
    \item Co-lead the writing of two successful grants worth US\$ 2'376'300 and US\$ 850'000.
    % \item Published [\ref{pub:alhakami2025towards}, \ref{pub:wang2024scaling}, \ref{pub:zhuge2025mindstorms}, \ref{pub:ashley2026racas}, \ref{pub:wang2024how}] based on work done.
    % \item Work location: King Abdullah University of Science and Technology, Thuwal 23955-6900, Kingdom of Saudi Arabia.
\end{rSubsection}

\begin{rSubsection}{Chief Technology Officer}{\rDateRange{2021-05-05}{}}{Perseverance Analytics Ltd.}
    \item Founding member of an incorporated non-profit data science startup based in Alberta, Canada.
    \item Startup focuses on connecting communities to social supports to bridge the gap between the availability and accessibility of services.
    % \item Work location: Remote.
\end{rSubsection}

\vfill\clearpage

\begin{rSubsection}{Doctoral Research Assistant}{\rDateRange{2021-01-04}{}}{Universit{\`{a}} della Svizzera italiana}
    \item Conducting research with Prof.\ J{\"{u}}rgen Schmidhuber on several deep learning topics.
    % \item Published [\ref{pub:zhuge2024agent}, \ref{pub:ashley2025distillation}, \ref{pub:strupl2021reward}, \ref{pub:strupl2025convergence}, \ref{pub:ventura2025upside}, \ref{pub:herrmann2024automatic}, \ref{pub:stanic2023languini}, \ref{pub:strupl2022upside}, \ref{pub:ashley2022learning}, \ref{pub:arulkumaran2022all}] based on work done.
    % \item Work location: Via la Santa 1, 6962 Lugano, Switzerland.
\end{rSubsection}

\begin{rSubsection}{Vice-President Academic}{\rDateRange{2019-05-01}{2020-04-30}}{Graduate Students' Association, University of Alberta}
    \item Salaried official representative of over 7,900 graduate students in academic matters.
    \item Advocated for graduate student issues to the university and worked with the university to build a better learning environment for students.
    \item Delivered several significant advocacy victories, including better oversight for mentorship and a reduced increment in tuition during a budgetary crisis.
    \item Time commitment of approximately 30 hours a week for a one-year term.
    % \item Work location: 1-49 Triffo Hall, University of Alberta, Edmonton, Alberta T6G 2E1, Canada.
\end{rSubsection}

\begin{rSubsection}{Graduate Research Assistant}{\rDateRange{2017-09-05}{2020-08-31}}{Reinforcement Learning and Artificial Intelligence Lab, University of Alberta}
    \item Conducted research with Prof.\ Richard S. Sutton and others on several reinforcement learning topics.
    % \item Published [\ref{pub:ashley2020understanding}, \ref{pub:ashley2019evolving}, \ref{pub:ashley2019artificial}, \ref{pub:ashley2021does}, \ref{pub:ma2020universal}] based on work done.
    % \item Work location: 116 St \& 85 Ave, University of Alberta, Edmonton, Alberta T6G 2R3, Canada.
\end{rSubsection}

\begin{rSubsection}{Undergraduate Summer Research Assistant}{\rDateRange{2015-05-01}{2017-08-31}}{University of Alberta}
    \item Won three separate competitive four-month NSERC Undergraduate Student Research Awards, the first working with first Prof.\ Jos{\'{e}} Nelson Amaral, and the latter two working with Prof.\ Richard S. Sutton.
    % \item Published [\ref{pub:sherstan2018comparing}, \ref{pub:amaral2018alberta}] based on work done.
    % \item Work location: 116 St \& 85 Ave, University of Alberta, Edmonton, Alberta T6G 2R3, Canada.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%   PEER-REVIEWED PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Peer-Reviewed Publications}

\begin{rPublications}
    \item \label{pub:dai2025efficient}
        Dai, Y.$^*$, Wang, Y.$^*$, \textbf{Ashley, D. R.}, \& Schmidhuber, J.
        (2026).
        Efficient Morphology-Control Co-Design via Stackelberg Proximal Policy Optimization.
        \textit{Proceedings of the 14th International Conference on Learning Representations.}
        \url{https://openreview.net/pdf?id=sJ0vOOkclw}
    \item \label{pub:alhakami2025towards}
        Alhakami, M.$^*$, \textbf{Ashley, D. R.}$^*$, Dunham, J.$^*$, Dai, Y., Faccio, F., Feron, F., \& Schmidhuber, J.
        (2025).
        Towards an Extremely Robust Baby Robot With Rich Interaction Ability for Advanced Machine Learning Algorithms.
        \textit{Proceedings of the 2025 IEEE/RSJ International Conference on Intelligent Robots and Systems.}
        \url{https://doi.org/10.1109/IROS60139.2025.11246188}

        \nopagebreak\vspace{-0.4em}\nopagebreak
        \textbf{Oral Presentation.}
        Previously presented as a late-breaking result at the 2024 IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS).
    \item \label{pub:zhuge2024agent}
        Zhuge, M., Zhao, C., \textbf{Ashley, D. R.}, Wang, W., Khizbullin, D., Xiong, Y., Liu, Z., Chang, E., Krishnamoorthi, R., Tian, Y., Shi, Y., Chandra, V., \& Schmidhuber, J.
        (2025).
        Agent-as-a-Judge: Evaluate Agents with Agents.
        \textit{Proceedings of the 42nd International Conference on Machine Learning.}
        \url{https://openreview.net/pdf?id=Nn9POI9Ekt}
    \item \label{pub:wang2024scaling}
        Wang, Y., Wu, Q., \textbf{Ashley, D. R.}, Faccio, F., Li, W., Huang, C., \& Schmidhuber, J.
        (2025).
        Scaling Value Iteration Networks to 5000 Layers for Extreme Long-Term Planning.
        \textit{Proceedings of the 42nd International Conference on Machine Learning.}
        \url{https://openreview.net/pdf?id=YwltsnSUFQ}

        \nopagebreak\vspace{-0.4em}\nopagebreak
        Previously presented at the 2024 European Workshop on Reinforcement Learning (EWRL).
    \item \label{pub:zhuge2025mindstorms}
        Zhuge, M.$^*$, Liu, H.$^*$, Faccio, F.$^*$, \textbf{Ashley, D. R.}$^*$, Csordas, R., Gopalakrishnan, A., Hamdi, A., Hammoud, H. A. A. K., Herrmann, V., Irie, K., Kirsch, L., Li, B., Li, G., Liu, S., Mai, J., Piekos, P., Ramesh, A., Schlag, I., Shi, W., Stanic, A., Wang, W., Wang, Y., Xu, M., Fan, D.-P., Ghanem, B., \& Schmidhuber, J.
        (2025).
        Mindstorms in natural language-based societies of mind.
        \textit{Computational Visual Media} \textbf{(IF 17.3)}, \textit{11}(1), 29--81.
        \url{https://doi.org/10.26599/CVM.2025.9450460}

        \nopagebreak\vspace{-0.4em}\nopagebreak
        Previously presented at the NeurIPS 2023 Workshop on Robustness of Zero/Few-Shot Learning in Foundation Models \textbf{(Best-paper Award)}.
    \item \label{pub:ashley2025distillation}
        \textbf{Ashley, D. R.}$^*$, Herrmann, V.$^*$, Friggstad, Z., \& Schmidhuber, J.
        (2025).
        On narrative information and the distillation of stories.
        \textit{IEEE Transactions on Pattern Analysis and Machine Intelligence} \textbf{(IF 20.8)}, \textit{47}(2), 697--707.
        \url{https://doi.org/10.1109/TPAMI.2024.3480702}

        \nopagebreak\vspace{-0.4em}\nopagebreak
        Previously presented at the NeurIPS 2023 Workshop on Machine Learning for Creativity and Design and at the NeurIPS 2022 Workshop Information-Theoretic Principles in Cognitive Systems.
    \item \label{pub:strupl2021reward}
        {\v{S}}trupl, M., Faccio, F., \textbf{Ashley, D. R.}, Srivastava, R. K., \& Schmidhuber, J.
        (2022).
        Reward-Weighted Regression Converges to a Global Optimum.
        \textit{Proceedings of the 36th AAAI Conference on Artificial Intelligence,} 8361--8369.
        \url{https://doi.org/10.1609/aaai.v36i8.20811}
    \item \label{pub:ashley2020understanding}
        \textbf{Ashley, D. R.}
        (2020).
        \textit{Understanding Forgetting in Artificial Neural Networks} [Master's thesis, University of Alberta].
        University of Alberta Education and Research Archive.
        \url{https://doi.org/10.7939/r3-6zvv-5z64}
    \item \label{pub:ashley2019evolving}
        \textbf{Ashley, D. R.}$^*$, Chockalingam, V.$^*$, Kuzma, B.$^*$, \& Bulitko, V.
        (2019).
        Learning to Select Mates in Evolving Non-playable Characters.
        \textit{Proceedings of the 2019 IEEE Conference on Games,} 1--8.
        \url{https://doi.org/10.1109/CIG.2019.8848114}
    \item \label{pub:ashley2019artificial}
        \textbf{Ashley, D. R.}$^*$, Chockalingam, V.$^*$, Kuzma, B.$^*$, \& Bulitko, V.
        (2019).
        Learning to Select Mates in Artificial Life.
        \textit{Proceedings of the Genetic and Evolutionary Computation Conference Companion,} 103--104.
        \url{https://doi.org/10.1145/3319619.3322060}
    \item \label{pub:sherstan2018comparing}
        Sherstan, C., \textbf{Ashley, D. R.}$^*$, Bennett, B.$^*$, Young, K., White, A., White, M., \& Sutton, R. S.
        (2018).
        Comparing Direct and Indirect Temporal-Difference Methods for Estimating the Variance of the Return.
        \textit{Proceedings of the 34th Conference on Uncertainty in Artificial Intelligence,} 63--72.
        \url{http://auai.org/uai2018/proceedings/papers/35.pdf}

        \nopagebreak\vspace{-0.4em}\nopagebreak
        \textbf{Oral Presentation.}
    \item \label{pub:amaral2018alberta}
        Amaral, J. N., Borin, E., \textbf{Ashley, D. R.}, Benedicto, C., Colp, E., Hoffmam, J. H. S., Karpoff, M., Ochoa, E., Redshaw, M., \& Rodrigues, R. E.
        (2018).
        The Alberta Workloads for the SPEC CPU 2017 Benchmark Suite.
        \textit{Proceedings of the 2018 IEEE International Symposium on Performance Analysis of Systems and Software,} 159--168.
        \url{https://doi.org/10.1109/ISPASS.2018.00029}
\end{rPublications}

\end{rSection}

%----------------------------------------------------------------------------------------
%   PREPRINTS AND TECHNICAL REPORTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Preprints and Technical Reports}

\begin{rPublications}
    \item \label{pub:ashley2026rpra}
        \textbf{Ashley, D. R.}, Le Lan, G., Zhao, C., Dhingra, N., Cai, Z., Chang, E., Zhuge, M., Shi, Y., Chandra, V., \& Schmidhuber, J.
        (2026).
        RPRA: Predicting an LLM-Judge for Efficient but Performant Inference.
        \url{https://arxiv.org/abs/2604.12634}

        \nopagebreak\vspace{-0.4em}\nopagebreak
        Under review.
        Previously presented at the ICLR 2026 Workshop on Multi-Agent Learning and Its Opportunities in the Era of Generative AI (RLDM) and the ICLR 2026 Workshop on Agentic AI in the Wild: From Hallucinations to Reliable Autonomy.
    \item \label{pub:ashley2026racas}
        \textbf{Ashley, D. R.}$^*$, Przepi{\'{o}}ra, J.$^*$, Chen, Y.$^*$, Abualsaud, A., Yesmagambet, N., Park, S., Feron, E., \& Schmidhuber, J.
        (2026).
        RACAS: Controlling Diverse Robots With a Single Agentic System.
        \url{https://arxiv.org/abs/2603.05621}

        \nopagebreak\vspace{-0.4em}\nopagebreak
        Under review.
    \item \label{pub:strupl2025convergence}
        {\v{S}}trupl, M., Szehr, O., Faccio, F., \textbf{Ashley, D. R.}, Srivastava, R. K., \& Schmidhuber, J.
        (2025).
        \textit{On the Convergence and Stability of Upside-Down Reinforcement Learning, Goal-Conditioned Supervised Learning, and Online Decision Transformers.}
        \url{https://arxiv.org/abs/2502.05672}

        \nopagebreak\vspace{-0.4em}\nopagebreak
        Under review.
    \item \label{pub:ventura2025upside}
        Di Ventura, J., \textbf{Ashley, D. R.}, Herrmann, V., Faccio, F., \& Schmidhuber, J.
        (2025).
        \textit{Upside Down Reinforcement Learning with Policy Generators.}
        \url{https://arxiv.org/abs/2501.16288}

        \nopagebreak\vspace{-0.4em}\nopagebreak
        Presented at the 2025 Multidisciplinary Conference on Reinforcement Learning and Decision Making (RLDM) and the 2025 European Workshop on Reinforcement Learning (EWRL).
    \item \label{pub:wang2024how}
        Wang, W., Alyahya, H. A., \textbf{Ashley, D. R.}, Serikov, O., Khizbullin, D., Faccio, F., \& Schmidhuber, J.
        (2024).
        \textit{How to Correctly do Semantic Backpropagation on Language-based Agentic Systems.}
        \url{http://arxiv.org/abs/2412.03624}

        \nopagebreak\vspace{-0.4em}\nopagebreak
        Under review.
    \item \label{pub:herrmann2024automatic}
        Herrmann, V.$^*$, \textbf{Ashley, D. R.}$^*$, \& Schmidhuber, J.
        (2024).
        \textit{Automatic Album Sequencing.}
        \url{https://arxiv.org/abs/2411.07772}

        \nopagebreak\vspace{-0.4em}\nopagebreak
        Presented as a late-breaking demo at the 2024 Conference of the International Society for Music Information Retrieval (ISMIR).
    \item \label{pub:stanic2023languini}
        Stanic, A.$^*$, \textbf{Ashley, D.}, Serikov, O., Kirsch, L., Faccio, F., Schmidhuber, J., Hofmann, T., \& Schlag, I.$^*$
        (2023).
        \textit{The languini kitchen: Enabling language modelling research at different scales of compute.}
        \url{https://arxiv.org/abs/2309.11197}
    \item \label{pub:strupl2022upside}
        {\v{S}}trupl, M., Faccio, F., \textbf{Ashley, D. R.}, Schmidhuber, J., \& Srivastava, R. K.
        (2022).
        \textit{Upside-Down Reinforcement Learning Can Diverge in Stochastic Environments With Episodic Resets.}
        \url{https://arxiv.org/abs/2205.06595}

        \nopagebreak\vspace{-0.4em}\nopagebreak
        Presented at the 2022 Multidisciplinary Conference on Reinforcement Learning and Decision Making (RLDM).
    \item \label{pub:ashley2022learning}
        \textbf{Ashley, D. R.}, Arulkumaran, K., Schmidhuber, J., \& Srivastava, R. K.
        (2022).
        \textit{Learning Relative Return Policies With Upside-Down Reinforcement Learning.}
        \url{https://arxiv.org/abs/2202.12742}

        \nopagebreak\vspace{-0.4em}\nopagebreak
        Presented at the 2022 Multidisciplinary Conference on Reinforcement Learning and Decision Making (RLDM).
    \item \label{pub:arulkumaran2022all}
        Arulkumaran, K., \textbf{Ashley, D. R.}, Schmidhuber, J., \& Srivastava, R. K.
        (2022).
        \textit{All You Need Is Supervised Learning: From Imitation Learning to Meta-RL With Upside Down RL.}
        \url{https://arxiv.org/abs/2202.11960}

        \nopagebreak\vspace{-0.4em}\nopagebreak
        Presented at the 2022 Multidisciplinary Conference on Reinforcement Learning and Decision Making (RLDM).
    \item \label{pub:ashley2021does}
        \textbf{Ashley, D. R.}, Ghiassian, S., \& Sutton, R. S.
        (2021).
        \textit{Does the Adam optimizer exacerbate catastrophic forgetting?}
        \url{https://arxiv.org/abs/2102.07686}
    \item \label{pub:ma2020universal}
        Ma, C., \textbf{Ashley, D. R.}, Wen, J., \& Bengio, Y.
        (2020).
        \textit{Universal successor features for transfer reinforcement learning.}
        \url{https://arxiv.org/abs/2001.04025}
\end{rPublications}

\end{rSection}

%----------------------------------------------------------------------------------------
%   AWARDS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Awards}

\rLine{Best-Paper Award}{NeurIPS 2023 R0-FoMo Workshop}{2023} \\
\rLine{Rising Star in AI Award}{King Abdullah University of Science and Technology}{2022} \\
\rLine{Queen Elizabeth II Graduate Scholarship}{University of Alberta (C\$10,800)}{2018} \\
\rLine{CGS-M}{Natural Science and Engineering Research Council of Canada (C\$17,500)}{2017} \\
\rLine{Walter H. Johns Graduate Fellowship}{University of Alberta (C\$5,800)}{2017} \\
\rLine{Science Graduate Scholarship}{University of Alberta (C\$2,000)}{2017} \\
\rLine{Kao Family Eisenco Scholarship}{University of Alberta (C\$1,200)}{2016} \\
\rLine{Jason Lang Scholarship}{University of Alberta (C\$1,000)}{2015} \\
\rLine{Suncor Energy Scholarship}{Suncor Energy (C\$1,800)}{2015} \\
\rLine{Jason Lang Scholarship}{University of Alberta (C\$1,000)}{2014} \\
\rLine{Suncor Energy Scholarship}{Suncor Energy (C\$1,800)}{2014}

\end{rSection}

%----------------------------------------------------------------------------------------
%   INVITED TALKS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Invited Talks}

\rLine{International Conference on Intelligent Robots and Systems}{Hangzhou, CN}{2025} \\
\rLine{NeurIPS 2023 R0-FoMo Workshop}{New Orleans, US}{2023} \\
\rLine{KAUST Rising Stars in AI Symposium}{Thuwal, SA}{2022} \\
\rLine{Alberta Machine Intelligence Institute Tea Time Talks}{Virtual}{2021} \\
\rLine{Canadian Association for Graduate Studies Conference}{Halifax, CA}{2019} \\
\rLine{IEEE Conference on Games}{London, GB}{2019} \\
\rLine{Chinese Graduate Students Association Workshop}{Edmonton, CA}{2019} \\
\rLine{Kindred}{Toronto, CA}{2018}

\end{rSection}

%----------------------------------------------------------------------------------------
%   SERVICE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Service}

\rLine{Reviewer}{Conference on Language Modeling}{2026} \\
\rLine{Reviewer}{International Conference on Intelligent Robots and Systems}{2026} \\
\rLine{Reviewer}{International Conference on Machine Learning}{2026} \\
\rLine{Reviewer}{ICLR Workshop on Multi-Agent Learning and Generative AI}{2026} \\
\rLine{Reviewer}{ICLR Workshop on Agentic AI in the Wild: Reliable Autonomy}{2026} \\
\rLine{Reviewer}{International Conference on Learning Representations}{2026} \\
\rLine{Reviewer}{AAAI Conference on Artificial Intelligence}{2026} \\
\rLine{Reviewer}{ICLR Workshop on World Models}{2025} \\
\rLine{Reviewer}{International Conference on Learning Representations}{2025} \\
\rLine{Reviewer}{European Workshop on Reinforcement Learning}{2024} \\
\rLine{Reviewer}{NeurIPS Workshop on Aligning RL Experimentalists and Theorists}{2024} \\
\rLine{Reviewer}{International Conference on Artificial Neural Networks}{2024} \\
\rLine{Reviewer}{Machine Learning}{2024} \\
\rLine{Program Committee Member}{European Workshop on Reinforcement Learning}{2023} \\
\rLine{Reviewer}{European Workshop on Reinforcement Learning}{2023} \\
\rLine{Reviewer}{ICML Workshop on Interactive Learning with Implicit Human Feedback}{2023} \\
\rLine{Reviewer}{Machine Learning}{2023} \\
\rLine{Faculty of Informatics Council}{Universit{\`{a}} della Svizzera italiana}{\rDateRange{2022}{2023}} \\
\rLine{Reviewer}{NeurIPS Workshop on Information-Theoretic Principles in Cognitive Systems}{2022} \\
\rLine{Reviewer}{NeurIPS Workshop on Reinforcement Learning for Real Life Workshop}{2022} \\
\rLine{Reviewer}{European Workshop on Reinforcement Learning}{2022} \\
\rLine{Mentoring Award Adjudication Panel}{University of Alberta}{2020} \\
\rLine{Equity, Diversity, and Inclusion Council}{Alberta Machine Intelligence Institute}{\rDateRange{2019}{2020}} \\
\rLine{Volunteer}{Campus Food Bank}{2019} \\
\rLine{Faculty of Graduate Studies and Research Council}{University of Alberta}{\rDateRange{2018}{2019}} \\
\rLine{Board Member}{Graduate Students' Association}{\rDateRange{2018}{2019}} \\
\rLine{Nominating Committee}{Graduate Students' Association}{\rDateRange{2018}{2019}} \\
\rLine{Council Member}{Graduate Students' Association}{\rDateRange{2018}{2020}}

\end{rSection}

%----------------------------------------------------------------------------------------
%   SUPERVISING SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Supervising}

\rLine{Jacopo di Ventura}{M.Sc. Student}{\rDateRange{2023}{2024}} \\
\rLine{James Jewitt}{High School Intern}{2015}

\end{rSection}

%----------------------------------------------------------------------------------------
%   TEACHING SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Teaching}

\rLine{Teaching Assistant}{Machine Learning}{2024} \\
\rLine{Teaching Assistant}{Machine Learning}{2023} \\
\rLine{Teaching Assistant}{Machine Learning}{2022} \\
\rLine{Teaching Assistant}{Algorithms \& Data Structures}{2022} \\
\rLine{Teaching Assistant}{Machine Learning}{2021} \\
\rLine{Teaching Assistant}{Introduction to File and Database Management}{2015}

\end{rSection}

%----------------------------------------------------------------------------------------
%   PROFESSIONAL MEMBERSHIP SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Professional Membership}

\rPlainLine{Association for Computing Machinery}{Since 2014} \\
\rPlainLine{Association for the Advancement of Artificial Intelligence}{Since 2018} \\
\rPlainLine{Institute of Electrical and Electronics Engineers}{Since 2019}

\end{rSection}

%----------------------------------------------------------------------------------------
%   NATURAL LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Natural Languages}

\begin{tabular}{ll}
    \rPair{English}{Native Speaker} & \rPair{French}{Moderate Fluency} \\
    \rPair{Italian}{Some Knowledge} & \rPair{Mandarin}{Some Knowledge}
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%   PROGRAMMING LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Programming Languages}

\begin{tabular}{llll}
    \rPair{Python}{Expert} & \rPair{Bash}{Strong} & \rPair{C/C++}{Strong} & \rPair{\LaTeX}{Strong} \\
    \rPair{Java}{Intermediate} & \rPair{SQL}{Intermediate} & \rPair{HTML}{Basic} & \rPair{Lisp}{Basic} \\
    \rPair{Prolog}{Basic}
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%   CITIZENSHIP AND RESIDENCE SECTION
%----------------------------------------------------------------------------------------

% \begin{rSection}{Citizenship and Residence}

% \begin{tabular}{lll}
%     \rPair{Canada}{Citizen} &
%     \rPair{South Africa}{Citizen} &
%     \rPair{Switzerland}{B Permit}
% \end{tabular}

% \end{rSection}

%----------------------------------------------------------------------------------------
%   CONFERENCE AND SUMMER SCHOOL ATTENDANCE SECTION
%----------------------------------------------------------------------------------------

% \begin{rSection}{Conference and Summer School Attendance}

% \rLine{International Conference on Learning Representations}{Rio de Janeiro, BR}{2026} \\
% \rLine{KAUST Rising Stars in AI Symposium}{Thuwal, SA}{2026} \\
% \rLine{International Conference on Intelligent Robots and Systems}{Hangzhou, CN}{2025} \\
% \rLine{International Conference on Machine Learning}{Vancouver, CA}{2025} \\
% \rLine{KAUST Rising Stars in AI Symposium}{Thuwal, SA}{2025} \\
% \rLine{International Society for Music Information Retrieval Conference}{San Francisco, US}{2024} \\
% \rLine{European Workshop on Reinforcement Learning}{Toulouse, FR}{2024} \\
% \rLine{International Conference on Intelligent Robots and Systems}{Abu Dhabi, AE}{2024} \\
% \rLine{CSCS Summer University on Effective High-Performance Computing}{Lugano, CH}{2024} \\
% \rLine{KAUST Rising Stars in AI Symposium}{Thuwal, SA}{2024} \\
% \rLine{Neural Information Processing Systems}{New Orleans, US}{2023} \\
% \rLine{European Workshop on Reinforcement Learning}{Brussels, BE}{2023} \\
% \rLine{Belgium-Netherlands Workshop on Reinforcement Learning}{Leiden, NL}{2023} \\
% \rLine{International Conference on Machine Learning}{Honolulu, US}{2023} \\
% \rLine{International Conference on Learning Representations}{Kigali, RW}{2023} \\
% \rLine{KAUST Rising Stars in AI Symposium}{Thuwal, SA}{2023} \\
% \rLine{Neural Information Processing Systems}{New Orleans, USA}{2022} \\
% \rLine{European Workshop on Reinforcement Learning}{Milan, IT}{2022} \\
% \rLine{Reinforcement Learning and Decision Making}{Providence, US}{2022} \\
% \rLine{KAUST Rising Stars in AI Symposium}{Thuwal, SA}{2022} \\
% \rLine{AAAI Conference on Artificial Intelligence}{Virtual}{2021} \\
% \rLine{Neural Information Processing Systems}{Virtual}{2020} \\
% \rLine{Canadian Association for Graduate Studies Conference}{Halifax, CA}{2019} \\
% \rLine{IEEE Conference on Games}{London, GB}{2019} \\
% \rLine{CIFAR Deep Learning and Reinforcement Learning Summer School}{Edmonton, CA}{2019} \\
% \rLine{Reinforcement Learning and Decision Making}{Montr{\'{e}}al, CA}{2019} \\
% \rLine{Chinese Graduate Students Association Workshop}{Edmonton, CA}{2019} \\
% \rLine{Reverse Expo}{Edmonton, CA}{2019} \\
% \rLine{Neural Information Processing Systems}{Montr{\'{e}}al, CA}{2018} \\
% \rLine{Artificial Intelligence and Interactive Digital Entertainment}{Edmonton, CA}{2018} \\
% \rLine{Uncertainty in Artificial Intelligence}{Monterey, US}{2018} \\
% \rLine{CIFAR Deep Learning and Reinforcement Learning Summer School}{Toronto, CA}{2018} \\
% \rLine{Accelerate AB}{Edmonton, CA}{2018}

% \end{rSection}

%----------------------------------------------------------------------------------------

\vfill
% \clearpage
% \null
% \vspace{0.475\textheight}
\begin{center}
    \large{\MakeUppercase{\bf References Available On Request}}
\end{center}

\end{document}
