%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Short Professional Resume
% LaTeX Template
% Version 2.1 2019-11-03
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Additional modifications by:
% Dylan Ashley
%
% Important note:
% This template requires the cv.cls file to be in the same directory as the
% .tex file. The cv.cls file provides the cv style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[letterpaper,dateabbrev,compact]{cv}

\name{Dylan Ashley}
\address{{\urlstyle{same} +41 78 213 19 50 ~ \\ ~ \href{mailto:mail@dylanashley.me}{mail@dylanashley.me} ~ \\ ~ \url{https://dylanashley.io}}}

\fancyfoot[C]{\thepage\ \ of\ \ \pageref{LastPage} \\ {\small Full curriculum vitae available at\enspace\url{https://dylanashley.io/assets/pdf/curriculum_vitae.pdf}}}
\addtolength{\textheight}{-\baselineskip}
\setbox0=\hbox{{\small\strut}}\addtolength{\textheight}{-\dp0}

\begin{document}

%----------------------------------------------------------------------------------------
%   EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Ph.D. in Informatics} \hfill \rDateRange{2021-01-04}{} \\[0.05em]
Universit{\`{a}} della Svizzera italiana (Dalle Molle Institute for Artificial Intelligence Research) \\[0.05em]
Supervisor: J{\"u}rgen Schmidhuber

%------------------------------------------------

{\bf M.Sc. in Computing Science} \hfill \rDateRange{2017-09-05}{2020-11-20} \\[0.05em]
University of Alberta (Alberta Machine Intelligence Institute) \\[0.05em]
Supervisor: Richard S. Sutton \textbf{(2024 Turing Award Recipient)}

%------------------------------------------------

{\bf B.Sc. Honors in Computing Science} \hfill \rDateRange{2013-09-04}{2017-06-13} \\[0.05em]
University of Alberta

\end{rSection}

%----------------------------------------------------------------------------------------
%   WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\rLine{Research Scientist Intern}{Meta Platforms, Inc.}{\rDateRange{2026-06-01}{2026-11-13}} \\
\rLine{Research Scientist Intern}{Meta Platforms, Inc.}{\rDateRange{2025-05-27}{2025-11-07}} \\
\rLine{Visiting Researcher}{King Abdullah University of Science and Technology}{\rDateRange{2023-01-22}{}} \\
\rLine{Chief Technology Officer}{Perseverance Analytics Ltd.}{\rDateRange{2021-05-05}{}} \\
\rLine{Doctoral Research Assistant}{Universit{\`{a}} della Svizzera italiana}{\rDateRange{2021-01-04}{}} \\
\rLine{Vice-President Academic}{Graduate Students' Association}{\rDateRange{2019-05-01}{2020-04-30}} \\
\rLine{Graduate Research Assistant}{University of Alberta}{\rDateRange{2017-09-05}{2020-08-31}} \\
\rLine{Undergraduate Summer Research Assistant}{University of Alberta}{\rDateRange{2015-05-01}{2017-08-31}}

\end{rSection}

%----------------------------------------------------------------------------------------
%   SELECTED PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Selected Publications}

\textit{A selection of recent works taken from twelve (12) authored peer-reviewed publications and eleven (11) additional authored preprints and technical reports:}
\vspace{0.25em}
\begin{rSelectedPublications}
    \item
        Dai, Y.$^*$, Wang, Y.$^*$, \textbf{Ashley, D. R.}, et al.
        (2026).
        Efficient Morphology-Control Co-Design via Stackelberg Proximal Policy Optimization.
        \textit{Proceedings of the 14th International Conference on Learning Representations.}
    \item
        \textbf{Ashley, D. R.}, et al.
        (2026).
        RPRA: Predicting an LLM-Judge for Efficient but Performant Inference.
        \textit{Under review.}
    \item
        \textbf{Ashley, D. R.}$^*$, Przepi{\'{o}}ra, J.$^*$, Chen, Y.$^*$, et al.
        (2026).
        RACAS: Controlling Diverse Robots With a Single Agentic System.
        \textit{Under review.}
    \item
        Zhuge, M., Zhao, C., \textbf{Ashley, D. R.}, et al.
        (2025).
        Agent-as-a-Judge: Evaluate Agents with Agents.
        \textit{Proceedings of the 42nd International Conference on Machine Learning.}
    \item
        Wang, Y., Wu, Q., \textbf{Ashley, D. R.}, et al.
        (2025).
        Scaling Value Iteration Networks to 5000 Layers for Extreme Long-Term Planning.
        \textit{Proceedings of the 42nd International Conference on Machine Learning.}
    \item
        Alhakami, M.$^*$, \textbf{Ashley, D. R.}$^*$, Dunham, J.$^*$, et al.
        (2025).
        Towards an Extremely Robust Baby Robot With Rich Interaction Ability for Advanced Machine Learning Algorithms.
        \textit{Proceedings of the 2025 IEEE/RSJ International Conference on Intelligent Robots and Systems.}
        \textbf{Oral Presentation.}
    \item
        \textbf{Ashley, D. R.}$^*$, Herrmann, V.$^*$, et al.
        (2025).
        On narrative information and the distillation of stories.
        \textit{IEEE Transactions on Pattern Analysis and Machine Intelligence} \textbf{(IF 20.8)}.
    \item
        Zhuge, M.$^*$, Liu, H.$^*$, Faccio, F.$^*$, \textbf{Ashley, D. R.}$^*$, et al.
        (2025).
        Mindstorms in natural language-based societies of mind.
        \textit{Computational Visual Media} \textbf{(IF 17.3)}.
\end{rSelectedPublications}

\end{rSection}

%----------------------------------------------------------------------------------------
%   AWARDS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Selected Awards}

\rLine{Best-Paper Award}{NeurIPS 2023 R0-FoMo Workshop}{2023} \\
\rLine{Rising Star in AI Award}{King Abdullah University of Science and Technology}{2022} \\
\rLine{Queen Elizabeth II Graduate Scholarship}{University of Alberta (C\$10,800)}{2018} \\
\rLine{CGS-M}{Natural Science and Engineering Research Council of Canada (C\$17,500)}{2017} \\
\rLine{Walter H. Johns Graduate Fellowship}{University of Alberta (C\$5,800)}{2017}

\end{rSection}

%----------------------------------------------------------------------------------------
%   RECENT SERVICE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Recent Service (\rDateRange{2026}{})}

\rLine{Reviewer}{Conference on Language Modeling}{2026} \\
\rLine{Reviewer}{International Conference on Intelligent Robots and Systems}{2026} \\
\rLine{Reviewer}{International Conference on Machine Learning}{2026} \\
\rLine{Reviewer}{ICLR Workshop on Multi-Agent Learning and Generative AI}{2026} \\
\rLine{Reviewer}{ICLR Workshop on Agentic AI in the Wild: Reliable Autonomy}{2026} \\
\rLine{Reviewer}{International Conference on Learning Representations}{2026} \\
\rLine{Reviewer}{AAAI Conference on Artificial Intelligence}{2026}

\end{rSection}

%----------------------------------------------------------------------------------------
%   SUPERVISING SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Supervising}

\rLine{Jacopo di Ventura}{M.Sc. Student}{\rDateRange{2023}{2024}} \\
\rLine{James Jewitt}{High School Intern}{2015}

\end{rSection}

%----------------------------------------------------------------------------------------
%   NATURAL LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Natural Languages}

\begin{tabular}{llll}
    \rPair{English}{Native} & \rPair{French}{Moderate} &
    \rPair{Italian}{Some Knowledge} & \rPair{Mandarin}{Some Knowledge}
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------

\vfill
\begin{center}
    \large{\MakeUppercase{\bf References Available On Request}}
\end{center}

\end{document}
